Legends for supplementary material

### 2019-05-09 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

**Supplementary Figure 1. Distance densities from centers of genomic bins to closest annotation.** Density curves of the distances (in millions of base pairs) from the center of genomic bins to the center of the nearest respective annotation for the GM12878 (left column) and K562 (right column) cell lines respectively. Each curve represents the raw (red) and $log_{2}$ transformed (blue) distance profiles for each annotation, across each of the 4 resolutions (A-D).

>>>>

**Supplementary Figure 1. GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb. (E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.

**Supplementary Figure 2. K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb. (E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
